Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-08 appendix.tex
Commit 2023-11-08 20:14

@@

{\centering \includegraphics[width=0.7\linewidth]{./images/LongtermTrends-5}

}

@@

@@

{\centering \includegraphics[width=0.7\linewidth]{./images/LongtermTrends-8}

}

@@

{\centering \includegraphics[width=1\linewidth]{./images/SzaTrendsSeasTogether-2}

}

\caption{Seasonal distribution of the SDR's long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$), the trends were computed with SZA bins of $1^\circ$, before and after local noon. Bins where $p<0.005$ or with less than 85 data points may be missing from view.}\label{fig:SZAtrendSeason}
\end{figure}

>>>>

\section[\appendixname~\thesection]{} % test

\  \

@@

{\centering \includegraphics[width=0.7\linewidth]{./images/LongtermTrends-5}}

@@

\  \

@@

{\centering \includegraphics[width=0.7\linewidth]{./images/LongtermTrends-8}}

@@

{\centering \includegraphics[width=1\linewidth]{./images/SzaTrendsSeasTogether-2}}

\caption{Long term trends of SDR as a function of SZA separately form morning and afternoon
periods, by season (rows of plots) for the three sky conditions (columns of plots).
Solid shapes represent statistical significant trends ($p<0.005$).
Cases where $p<0.005$ or with less than $85$ observations may be missing from view.}\label{fig:SZAtrendSeason}
\end{figure}

\ \
